\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-29 Paper/Paper.tex
again
cont.

	Table~\ref{tb:OCT_test} and Table~\ref{tb:Fundus_test} show the predictive values on the test dataset. Fig.~\ref{fig:A_ROC} shows the ROCs of each abnormity. The results show that the performance of the OCT Model is significantly better than that of the Fundus Model. Fundus abnormities tend to be less prominent, since the abnormity on fundus image are usually quite small and scattered. Moreover, one fundus image usually contains more than one abnormities, while most OCT images contain only one abnormity on each image. Also given that we have less fundus images than OCT ones, the difficulties for fundus classification increases.

@@

	The confusion matrices are shown in Fig.~\ref{fig:A_conf_mat}) and the t-SNE graphs are shown in Fig.~\ref{fig:A_tSNE}. During training, most of the abnormities are well-separated. However, this is not the case during testing. On the t-SNE graph, the OCT Model still shows clear separation of clusters, many of which, however, are mingled with data points that do not belong to the cluster. This is because some OCT abnormities resemble each other. For example, ``IF'', ``DME'' and ``Mactel'' may look very similar. As to the Fundus Model, there are fewer small distinct clusters and there is a large cluster instead. This is likely due to the fact that many fundus images contain multiple abnormities. For example, a patient with the disease ``rDR'' shows the abnormities ``CWP'', ``HE'', ``HM'' and ``VA''. Therefore, many abnormities tend to appear together, impeding classification of abnormities.

>>>>

	Table~\ref{tb:OCT_test} and Table~\ref{tb:Fundus_test} show the predictive values on the test dataset. Fig.~\ref{fig:A_ROC} shows the ROCs, Fig.~\ref{fig:A_conf_mat} shows the confusion matrices and Fig.~\ref{fig:A_tSNE} shows the t-SNE graphs for each abnormity.

	The OCT Model tends to be overfitting, while the Fundus Model cannot reach a satisfying level in terms of DL. Overall, the performance of the OCT Model is significantly better than that of the Fundus Model.

	Fundus abnormities tend to be less prominent than those of OCT, since the abnormity in fundus image are usually quite small and scattered. Moreover, one fundus image usually contains more than one abnormity, while most OCT images contain only one abnormity on each image. Also given that we have less fundus images than OCT ones, the difficulties for fundus classification increases.

@@
